Inferring Invariants of Distributed Programs

### 2015-05-01 Doc/introback.tex
some minor

Building a reliable distributed system is a difficult task, since distributed system should continue operating even when components or the network fail, this means that there are many corner cases that developers should consider when building a system. Building such 
a reliable and dependable system is not possible without thorough testing. However, testing a distributed system is a difficult task because it is hard to test components of a distributed system in isolation. There are many 
failure scenarios that a distributed system should handle and these scenarios should be tested as well. In some cases reproducing the failures is a difficult task e.g., degrading network performance for test purposes. Many bugs turn out to be heisenbugs in a distributed 
system which are hard to reproduce and debug. Debugging and testing distributed systems is hard because a fault in a single node is not confined to that node, instead, it may cause an error in another node. In fact errors in distributed system should be defined on global state of the system and not on a single node. This also makes program comprehension of distributed systems a difficult task, since the developer needs to comprehend interaction of different nodes as well as logic of each node.

To test and debug distributed systems, developers and testers have to spend a considerable amount of time inspecting logs of the system manually and look for incidents the system does not behave as 
expected. One alternative to this laborious approach is to define invariants for a system's expected behaviour and check the software traces against these invariants. This approach is considerably easier than the former but as the system gets larger and more 
complex, providing invariants manually becomes more difficult. In this work, we automate the process of defining invariants for systems by inferring likely invariants of distributed systems from run time execution of systems. We define an invariant of distributed systems as a property that holds at a certain consistent cut across multiple nodes in distributed state of a distributed program. These inferred invariants can ease many programming tasks, such as program comprehension, bug prevention, debugging, verification and testing. Inferred invariants can show specification of systems,  act as documentation and help program comprehension. They can be checked after each modification to source code to make sure that invariants of the system that implies its correctness are not violated, thus helping bug prevention. Even if the bugs get into the system, these invariants can help debugging by locating the points in program that they got violated. Moreover, they can be written in form of assertions and be used for automated test generation. 
%Ernst et al \cite{ernst2007daikon} define a program invariant as ``a property that holds at a certain point or points in a program".

@@

\begin{figure}
\centering
\begin{lstlisting}[caption={Coordinator Code}]
for i := 1 to n do
	send('Query',i)
commit := decide()
for i:= 1 to n do
	recv(buf,i)
	if (buf == 'Abort')
		commit := 'Abort'
for i := 1 to n
	send(commit, i)
\end{lstlisting}
\begin{lstlisting}[caption={Replica Code}]
recv(buf)
if(buf == 'Query')
	vote:= decide()
	send(vote)
if (vote == 'Abort')
	commit = 'Abort'
else
	recv(buf)
	commit = buf
\end{lstlisting}
\caption{Pseudo two phase commit code for coordinator and replicas}
\label{lst:2pc}
\end{figure}

In this work we 
assume that state of each node is comprised of its variables. Not all variables of one node is affected by other nodes, we define the set of variables of one node whose values are affected by other nodes as distributed state variables of that node. We refer to set of distributed 
state variables of all nodes as distributed state of the system. We use Daikon \cite{ernst2001dynamically} to infer invariants between variables, so we can infer linear ($y = ax + b$), ordering ($y < x$) and containment ($x \in y$) relationships that may hold between the distributed state variables of all nodes in the system.

>>>>

Building a reliable distributed system is a difficult task, since distributed system should continue operating even when components or the network fail, this means that there are many corner cases that developers should consider when building a system. Building such 
a reliable and dependable system is not possible without thorough testing. However, testing a distributed system is a difficult task because it is hard to test components of a distributed system in isolation. There are many 
failure scenarios that a distributed system should handle and these scenarios should be tested as well. In some cases reproducing the failures is a difficult task e.g., degrading network performance for test purposes. Many bugs turn out to be heisenbugs in a distributed 
system which are hard to reproduce and debug. Debugging and testing distributed systems is hard because a fault in a single node is not confined to that node, instead, it may cause an error in another node. In fact errors in distributed system should be defined on global state of the system and not on a single node. This also makes program comprehension of distributed systems a difficult task, since the developer needs to comprehend interaction of different nodes as well as the logic of each node.

To test and debug distributed systems, developers and testers have to spend a considerable amount of time inspecting logs of the system manually and look for incidents the system does not behave as 
expected. One alternative to this laborious approach is to define invariants for a system's expected behaviour and check the software traces against these invariants. This approach is considerably easier than the former but as the system gets larger and more 
complex, providing invariants manually becomes more difficult. In this work, we automate the process of defining invariants by inferring likely invariants of distributed systems from run time execution. We define an invariant of distributed systems as a property that holds at a certain consistent cut across multiple nodes in distributed state of a distributed system. These inferred invariants can ease many programming tasks, such as program comprehension, bug prevention, debugging, verification and testing. Inferred invariants can show specification of systems,  act as documentation and help program comprehension. They can be checked after each modification to source code to make sure that invariants of the system that implies its correctness are not violated, thus helping bug prevention. Even if the bugs get into the system, these invariants can help debugging by locating the points in program that they got violated. Moreover, they can be written in form of assertions and be used for automated test generation. 
%Ernst et al \cite{ernst2007daikon} define a program invariant as ``a property that holds at a certain point or points in a program".

@@

\begin{figure}
\centering
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[caption={Coordinator Code}]
for i := 1 to n do
	send('Query',i)
commit := decide()
for i:= 1 to n do
	recv(buf,i)
	if (buf == 'Abort')
		commit := 'Abort'
for i := 1 to n
	send(commit, i)
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[caption={Replica Code}]
recv(buf)
if(buf == 'Query')
	vote:= decide()
	send(vote)
if (vote == 'Abort')
	commit = 'Abort'
else
	recv(buf)
	commit = buf
\end{lstlisting}
\end{minipage}\hfill
\caption{Pseudo two phase commit code for coordinator and replicas}
\label{lst:2pc}
\end{figure}

%\begin{figure}
%\centering
%\begin{lstlisting}[caption={Coordinator Code}]
%for i := 1 to n do
%	send('Query',i)
%commit := decide()
%for i:= 1 to n do
%	recv(buf,i)
%	if (buf == 'Abort')
%		commit := 'Abort'
%for i := 1 to n
%	send(commit, i)
%\end{lstlisting}
%\begin{lstlisting}[caption={Replica Code}]
%recv(buf)
%if(buf == 'Query')
%	vote:= decide()
%	send(vote)
%if (vote == 'Abort')
%	commit = 'Abort'
%else
%	recv(buf)
%	commit = buf
%\end{lstlisting}
%\caption{Pseudo two phase commit code for coordinator and replicas}
%\label{lst:2pc}
%\end{figure}

In this work we 
assume that state of each node is comprised of its variables. Not all variables of one node is affected by other nodes, we define the set of variables of one node whose values are affected by other nodes as distributed state variables of that node. We refer to the set of distributed 
state variables of all nodes as distributed state of the system. We use Daikon \cite{ernst2001dynamically} to infer invariants between variables, so we can infer linear ($y = ax + b$) and ordering ($y < x$) relationships that may hold between the distributed state variables of all nodes in the system.
